---
title: "Benchmark chunks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{benchmark}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

`hook_benchmark` adds the benchmark feature to chunks.
To benchmark a chunk, specifying `benchmark=TRUE` as a chunk option.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Basic usage

```{r setup}
library(chunkhooks)
hook_benchmark()
```

```{r bench1, benchmark=TRUE}
# benchmark=TRUE is specified as a chunk option
sum(seq(100))
```

As the above result shows, output format contains chunk label.
I recommend specifying chunk options explicitly.
Note that this function is experimental, and format may change in the future.

# Fomatting results

If you do not like the default formatting, you may provide original function to
the `format` argument.
The function takes a result of a benchmark in seconds as the first argument,
and a list of current chunk options as the second argument.
The example below shows the benchmark result as is.
Make sure the formatting function returns a string.

```{r}
hook_benchmark(format = function(x, options) as.character(x))
```

```{r bench2, benchmark=TRUE}
sum(seq(100))
```

# Insert results in body text

If you need to insert the result with the text, use `chunkhooks::benchmarks` environment.
This environment records all the benchmark results in seconds.
You can extract a result by specifying a chunk label.

For example, `` `r 'r'` benchmarks$bench1 `` gives `r benchmarks$bench1`.

